251 MA

### 2023-02-27 code/process.Rmd
work on checking inputs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
theme_set(theme_bw())

@@

```
<!--
# Exclusions

```{r}
d |> group_by(status) |> tally()

@@

d_check_nas |> select(-sub_rep, -subfield) |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N) |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
```

@@

```{r}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="bernoulli",
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        iter=100,
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

@@

```{r, eval=F}
tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                           z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family="bernoulli",
                        data=data_tier3,
                        file=here(model_location, "tier3_porig"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

theme_set(theme_bw())

@@

d |> tally()
d |> group_by(status) |> tally()

@@

d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
                      sub_rep, subfield,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N) |> filter(if_any(everything(), ~is.na(.))) #|> nrow()

@@

d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
                      sub_rep, subfield,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
```

@@

```{r, eval=F}
tier1_subjective <- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        #family=gaussian(link='logit'), # runs
                        #family="cumulative", # runs on 1-5 data
                        # family="zero_one_inflated_beta", runs, 
                        # beta_binomial on 0-4 data
                        data=data_tier1,
                        #file=here(model_location, "tier1_subjective"),
                        prior=priors, 
                        iter=100,
                        control=list(adapt_delta=.99),
                        #backend="cmdstanr"
                        )
```

@@

```{r, eval=F}
tier3_porig <- brm(p_orig ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                           z_target_d_calc + z_log_p+ 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                             z_target_d_calc + z_log_p| academic_year),
                        family=(link="logit"),
                        data=data_tier3,
                        file=here(model_location, "tier3_porig"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        #backend="cmdstanr"
                   )
```
